Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-01-29 cav2017/cav2017.tex
nuge

\begin{figure}
\centering
{\scriptsize
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ % \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
   \& 
   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesize};
       %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
       %\node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
       %\node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc SAT};
       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc SAT};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& complexnode/.pic={
     \coordinate (auxsynth);
     \node[draw,rectangle,align=center] (KSAT) at ([xshift=0cm]auxsynth.center) {Prog.\\Search};
     \node[draw=none] (SATK) at ([xshift=-.7cm,yshift=1.5cm]KSAT)  {{\sc Inputs}};
     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$K$};
    }
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
    }\\
   \&
   \& complexnode/.pic={
     \coordinate (UNSAT);
     \coordinate (KUNSAT)  at ([xshift=0cm]UNSAT.center);
     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT};
  }
  \& \& \coordinate (FAIL);\\
  };
  \path
    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
    (abstract.south) edge node{$(\phi(K), \vec{k})$} (synth.north)
    %([yshift=2em]synth.east) edge node {Candidate} ([yshift=2em]verif.west)
    %([yshift=-2em]verif.west) edge node {New input} ([yshift=-2em]synth.east)
    %([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif.west)
    %([yshift=-2em]verif.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
    %([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
    %(AAC) edge[bend right] node[align=center] {$k$} (AAI.north)
    %([xshift=-4.9cm]verify.south) edge node[align=center] {$\mat{A},\mat{B}$\\$\phi$} (AAI.north)
    %(AAI.east) edge (AAV.west)
    ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
    ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east)
    (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
    %(AAC.west) edge (AB.west)
    %(verify.north) edge (counter.south)
    %(counter.west) edge (abstract.east)
    %(counter.south west) edge (synth.north east)
    (FAIL.north) edge (done.south)
    ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
  \path[-] 
     (KSAT.south) edge (KUNSAT.north)
     (KUNSAT.east) edge (FAIL.west)
     (verify.north) edge node {$(k,x_0)$} (aux);
\end{tikzpicture}
}
\caption{Abstraction-based CEGIS.}
\label{fig:CEGARIS} 
\end{figure}

>>>>

\begin{figure}
\centering
{\scriptsize
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ % \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
   \& 
   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
       %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
       %\node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
       %\node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc SAT};
       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& complexnode/.pic={
     \coordinate (auxsynth);
     \node[draw,rectangle,align=center] (KSAT) at ([xshift=0cm]auxsynth.center) {Program\\Search};
     \node[draw=none] (SATK) at ([xshift=-.7cm,yshift=1.5cm]KSAT)  {{$\phi(K,k)$}};
     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$K$};
    }
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
    }\\
   \&
   \& complexnode/.pic={
     \coordinate (UNSAT);
     \coordinate (KUNSAT)  at ([xshift=0cm]UNSAT.center);
     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT\\ (No Candidate Found)};
  }
  \& \& \coordinate (FAIL);\\
  };
  \path
    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
    (abstract.south) edge node{$(\phi(K), \vec{k})$} (synth.north)
    %([yshift=2em]synth.east) edge node {Candidate} ([yshift=2em]verif.west)
    %([yshift=-2em]verif.west) edge node {New input} ([yshift=-2em]synth.east)
    %([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif.west)
    %([yshift=-2em]verif.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
    %([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
    %(AAC) edge[bend right] node[align=center] {$k$} (AAI.north)
    %([xshift=-4.9cm]verify.south) edge node[align=center] {$\mat{A},\mat{B}$\\$\phi$} (AAI.north)
    %(AAI.east) edge (AAV.west)
    ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
    ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east)
    (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
    %(AAC.west) edge (AB.west)
    %(verify.north) edge (counter.south)
    %(counter.west) edge (abstract.east)
    %(counter.south west) edge (synth.north east)
    (FAIL.north) edge (done.south)
    ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
  \path[-] 
     (KSAT.south) edge (KUNSAT.north)
     (KUNSAT.east) edge (FAIL.west)
     (verify.north) edge node {$(k,x_0)$} (aux);
\end{tikzpicture}
}
\caption{Abstraction-based CEGIS.}
\label{fig:CEGARIS} 
\end{figure}

### 2017-01-29 hscc2017/paper.tex

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses the $\mu$-calculus to
directly model the digital controller so that the selected parameters are
stable by design.  Most work in verification focuses on finding a correct
variant of a known controller, looking for optimal parameter
representations using FWL, but ignore the effects of rounding errors due to
issues of mathematical tractability.  The analyses
in~\cite{DBLP:conf/hybrid/WangGRJF16, DBLP:conf/hybrid/RouxJG15} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of existing code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.  If~the error of the
implementation is lower than this tolerance level, then the verification is
successful.

>>>>

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A~recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses the $\mu$-calculus to
directly model the digital controller so that the selected parameters are
stable by design.  Most work in verification focuses on finding a correct
variant of a known controller, looking for optimal parameter
representations using FWL, but ignore the effects of rounding errors due to
issues of mathematical tractability.  The analyses
in~\cite{DBLP:conf/hybrid/WangGRJF16, DBLP:conf/hybrid/RouxJG15} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of existing code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.  If~the error of the
implementation is lower than this tolerance level, then the verification is
successful.
